The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
update winpos discussion

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength varied in winter layers becoming stable at ~200 m and remained
consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in
winter layers increased between ~10 m and ~50 m observations, remaining stable with
additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with fix
for open/rerun --> Like coarse landcover resolution (above), low numbers of
observations were not sufficient for capturing individuals in all contexts and
therefore layer similarity could not be calculated below approximately <!--TODO:
update these -->75 observations for forest, approximately 210 observations for
open and approximately 300 observations for forage (Figure \@ref(fig:nobs)c).
Once sufficient observations were obtained, layer similarity stabilized for all
three landcover classes at approximately 200 observations for forest and
approximately 300 observations for open and forage landcover types. Connective
redundancy increased dramatically between ~10 m and ~50 m observations before
stabilizing with all new observations included (Figure \@ref(fig:nobs)d). Given
the observed trend of these multilayer metrics stabilizing after a certain
number of observations are included, the results suggest this sensitivity method
could be useful for determining the number of observations necessary for
sufficiently describing social dynamics across contexts.

@@

<!-- TODO: update.....-->
Contrasting winter and summer seasons became more similar with increasing window
length. Individual graph strength and layer relevance increased for all summer
layers as individuals became more connected with increasing window lengths
(Figure \@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). Layer similarity between
seasons increased consistently across landcover class (Figure
\@ref(fig:winlen)b).  These results suggest that an increasing window length,
especially for the summer season, may be resulting in less precisely defined
seasons that are not clearly capturing periods of aggregation and
dissaggregation related to resource availability.

<!-- TODO: end with something highlighting this shows it's
important to properly define your season -->

>>>>

As the number of observations used to generate multilayer networks increased,
individuals became more connected and metrics appeared to stabilize. Mean graph
strength varied in winter layers becoming stable at ~200 m and remained
consistently weak in summer layers (Figure \@ref(fig:nobs)a). Layer relevance in
winter layers increased between ~10 m and ~50 m observations, remaining stable
with additional observations (Figure \@ref(fig:nobs)b). <!-- TODO: update with
fix for open/rerun --> Like coarse landcover resolution (Figure
\@ref(fig:lcres)), low numbers of observations were not sufficient for capturing
individuals in all contexts and therefore layer similarity could not be
calculated below approximately <!--TODO: update these -->75 observations for
forest, approximately 210 observations for open and approximately 300
observations for forage (Figure \@ref(fig:nobs)c). Once sufficient observations
were obtained, layer similarity stabilized for all three landcover classes at
approximately 200 observations for forest and approximately 300 observations for
open and forage landcover types. Connective redundancy increased dramatically
between ~10 m and ~50 m observations before stabilizing with all new
observations included (Figure \@ref(fig:nobs)d). Given the observed trend of
these multilayer metrics stabilizing after a certain number of observations are
included, the results suggest this sensitivity method could be useful for
determining the number of observations necessary for sufficiently describing
social dynamics across contexts.

@@

<!-- TODO: this first sentence is not about layer similarity - so hopefully it isn't
guiding the reader the wrong way -->
Contrasting seasons of sociality become more similarly connected with window
length. Mean graph strength and layer relevance increased for summer layers as
individuals became more connected with increasing window lengths (Figure
\@ref(fig:winlen)a, Figure \@ref(fig:winlen)b). In contrast, mean graph strength
and layer relevance was relatively stable for winter layers. Similarity of
layers across habitat classes and between seasons (e.g. open summer compared to
open winter) was variable across window lengths (Figure \@ref(fig:winlen)c).
Connective redundancy increased marginally with increasing window length. These
results suggest that an increasing window length, especially for the summer
season, may be resulting in less precisely defined seasons that are not clearly
capturing periods of aggregation and dissaggregation related to resource
availability.
